Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-27 paper/current/main.tex
an extra interesting reference

Globally, science has experienced many changes, from gradual globalization to the more sudden 2017 U.S. travel bans. 
The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact}.
Given mobility's importance, its vital that we gain a better understanding of where, how, and why researchers move, and what the impact of these movements will be. 
With this new data-driven approach to learning distances relating to mobility, we capture the latent and nuanced structure of mobility at multiple scales;
with this, predictive models can be improved and new insights gained, which in turn will inform more effective science and immigration policy, allowing global science to dictate the terms and leverage the benefits of our own migrations.

>>>>

Globally, science has experienced many changes, from gradual globalization to the more sudden 2017 U.S. travel bans. 
The consequences of these changes are far-reaching, and how nations respond to them will shape the future of the scientific enterprise~\autocite{chinchilla2018travelban, wagner2017open, sugimoto2017mostimpact, whetsell2019democracy}.
Given mobility's importance, its vital that we gain a better understanding of where, how, and why researchers move, and what the impact of these movements will be. 
With this new data-driven approach to learning distances relating to mobility, we capture the latent and nuanced structure of mobility at multiple scales;
with this, predictive models can be improved and new insights gained, which in turn will inform more effective science and immigration policy, allowing global science to dictate the terms and leverage the benefits of our own migrations.
